Component response rate variation drives stability in large complex systems

### 2018-05-21 SI.Rmd
Fix subtitles

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#Incr_S}) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Feasilbility of complex systems](#Feasibility)

@@

**Competition** {#competition}

@@

**Mutualism** {#mutualism}

@@

**Predator-prey** {#pred-prey}

@@

>>>>

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#Incr_S}) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Feasilbility of complex systems](#Feasibility) 
- [Genetic algorithm](#ga)

@@

<a name="competition">**Competition**</a>

@@

<a name="mutualism">**Mutualism**</a>

@@

<a name="pred-prey">**Predator-prey**</a>

@@

Genetic algorithm {#ga}
================================================================================
